\documentclass[12pt,letterpaper]{article}
\usepackage[ampersand]{easylist}
\usepackage[margin=1in]{geometry}
\usepackage{requirements}
\usepackage{float}
\usepackage{amsmath}
\bibliography{Bibliography.bib}
%% @DocumentRequirement (1.1,"Title")
\title{Requirements}
%% @DocumentRequirement (1.3,"Team #")
\team{1}
%% @DocumentRequirement (1.4,"Team Members")
\author{Alex Chaloux, Alex Wortham, Asanga Bandara, Doug Bouler}
%% @DocumentRequirement (1.5,"Customer")
\customer{EPRI}

\begin{document}

%% @DocumentRequirement (1,"Title Page")
%% @DocumentRequirement (1.2,"Date")
\reqstitlepage

%% @DocumentRequirement (2,"Table of Contents")
\tableofcontents
\clearpage
\setstretch{2}

%% @DocumentRequirement (4,"Requirements")
\section{Requirements}

%% @DocumentRequirement (4.1,"Numbered list of requirements initially agreed to by team and customer.")
\begin{easylist}[articletoc] \requirements

& \req{weather}Weather Resistance.
	
	&& The product's electrical components must be protected by a NEMA Type 3R enclosure. (\href{https://www.nema.org/Products/Documents/nema-enclosure-types.pdf}{https://www.nema.org/Products/Documents/nema-enclosure-types.pdf})
	&& The product's components must comply with International Protection Marketing Code 25 (IP25. \href{http://www.dsmt.com/pdf/resources/iprating.pdf}{http://www.dsmt.com/pdf/resources/iprating.pdf}).

& \req{home view}User Interface -- Home view.
	
	&& The view has a ``Edit Configuration'' button.
		&&& When the user presses this button they are presented with the Product
		Configuration View \refreq{prod conf view}.
	&& The view lists all configured appliances in order of their assigned
	priority.
	&& Each appliance displays its state \refreq{appliance state}.
	&& \req{appliance state}Each appliance may be in exactly one of the following
	states at a given time.
		&&& Powered on.
		&&& Powered off.
	&& Appliances which are in the powered on state will display their current
	demand in kilowatts as a number.
	&& Pressing on an appliance will present the Appliance Usage History View.
	&& The view lists the current cost towards the current billing cycle.
	&& The view lists the predicted total cost towards the current billing cycle.
			
& \req{information}User Interface -- Information.

	&& \req{app usage history view}Appliance Usage History View.
		&&& The view displays the appliance's state.
		&&& Appliances which are in the powered on state will display their current
		demand in kilowatts as a number.
		&&& The view has a graph of the appliance's demand history by kilowatts.
			&&&& More specifics\ldots 
		&&& The view has a graph of the appliance's cost history.
			&&&& More specifics\ldots 
		&&& The view displays the appliance's current cost towards the current billing
		cycle.
		&&& The view displays the appliance's predicted total cost towards the current
		billing cycle.

& \req{behaviors}User Interface -- Configurable Behaviors.

	&& \req{adjust demand limits}Adjust Demand Limits View.
		&&& The view has a slider that controls the demand limit preference.
			&&&& The slider is scaled by dollar amounts.
			&&&& The minimum value of the slider is the calculated cost of the demand
			limit minimum \refreq{demand limit min}.
			&&&& The maximum value of the slider is the calculated cost of the demand
			limit maximum \refreq{demand limit max}.  
		&&& \req{demand limit min}The minimum value of the demand limit is the 
		greatest max demand of each individual appliance.
		&&& \req{demand limit max}The demand limit has a maximum value of the sum of
		all appliances' max demand.
		&&& The view has a ``Save Changes'' button.
			&&&& Pressing this button saves the demand limit preference to the database.
			&&&& Pressing this button returns the user to the Product Configuration View
			\refreq{prod conf view}.
		&&& The view has a ``Cancel'' button.
			&&&& Pressing this button returns the user to the Product Configuration View
			\refreq{prod conf view}.

& \req{configuration}User Interface -- Initial Configuration.

	&& \req{appliance types}The following types of appliances are available
	for configuration in the user interface.
	
		&&& Heating, ventilation, and air conditioning (HVAC) units.
		&&& Dish washers.
		&&& Water heaters.
		&&& Clothes dryers.
		
	&& \req{configure sensors view}Configure Sensors View.
	
		&&& The view lists all sensors connected to the controller.
		&&& Each sensor has a ``Edit'' button next to it.
			&&&& Pressing this button presents the Edit Sensor View \refreq{edit sensor
			view}.
		&&& The view has a ``Done'' button.
			&&&& Pressing this button returns the user to the Product Configuration View
			\refreq{prod conf view}.
			
	&& \req{edit sensor view}Edit Sensor View.

		&&& The view has a field for the user to set a name for the sensor.
		&&& The view has a field for the user to set the voltage of the circuit to
		which the sensor is attached.
		&&& The view has a field for the user to set the amperage of the breaker to
		which the sensor is attached.
		&&& The view has a ``Save Changes'' button.
			&&&& Pressing this button saves the sensor configuration to the database.
			&&&& Pressing this button returns the user to the Configure Sensors View
			\refreq{configure sensors view}. 
		&&& The view has a ``Cancel'' button.
			&&&& Pressing this button discards any changes the user has made.
			&&&& Pressing this button returns the user to the Configure Sensors View
			\refreq{configure sensors view}. 
		 
	&& \req{edit appliance view}Edit Appliance View.
	
		&&& The view contains a field to enter a user defined name for the appliance.
		&&& The view contains a drop down list to select the type of the appliance.
			&&&& The list contains all appliance types listed in requirement 
			\refreq{appliance types}.
			&&& The view displays the name of the sensor associated with the appliance.
		&&& The view contains a ``Save Changes'' button.
			&&&& Pressing this button saves the appliance configuration to the
			database.
			&&&& Pressing this button presents the Product Configuration View
			\refreq{prod conf view}.
		&&& The view contains a ``Cancel'' button.
			&&&& Pressing this button discards any changes the user has made.
			&&&& Pressing this button presents the Product Configuration View
			\refreq{prod conf view}.
		
	
	&& \req{delete app confirm view}Delete Appliance Confirmation View.
	
		&&& The view contains a warning message.
		&&& The view has a ``Yes, delete appliance.'' button.
			&&&& Pressing this button deletes the appliance from the database.
			&&&& Pressing this button presents the Product Configuration View
			\refreq{prod conf view}.
		&&& The view has a ``No, just kidding.'' button.
			&&&& Pressing this button presents the Product Configuration View
			\refreq{prod conf view}.
	
	&& \req{add appliance view}Add Appliance View.
	
		&&& All requirements from the Edit Appliance View \refreq{edit appliance view}
		are required by this view as well.
		&&& The view contains a drop down list to select the sensor to associate with
		the appliance.
			&&&& The list contains all configured sensors.
			&&&& Sensors which are not currently associated with an appliance are marked
			as ``Available''.
			&&&& Sensors which are associated with another appliance are greyed out.
			&&&& Sensors which are associated with another appliance display the name of
			the appliance to which they are associated.
		
	&& \req{prod conf view}Product Configuration View.
	
		&&& The view displays all currently configured appliances in order of their
		assigned priority.
		&&& Each appliance may be dragged and dropped to alter its priority.
		&&& The view has an ``Adjust Demand Limits'' button.
			&&&& When the user presses this button they are presented with the Adjust
			Demand Limits View \refreq{adjust demand limits}.
		&&& Each appliance has a ``Delete'' button.
			&&&& When the user presses one of these buttons they
		are presented with the Delete Appliance Confirmation View \refreq{delete app
		confirm view}.
		&&& Each appliance has an ``Edit'' button.
			&&&& When the user presses one of these buttons they are presented with the
			Edit Appliance View \refreq{edit appliance view}.
		&&& The view has an ``Add Appliance'' button.
			&&&& When the user presses this button they are presented
		with the Add Appliance View \refreq{add appliance view}.
		&&& The view has a ``Finished'' button.
			&&&& When the user presses this button the Home View \refreq{home view} is
			presented.
		&&& Thew view has a ``Configure Sensors'' button.
			&&&& When the user presses this button the Configure Sensors View
			\refreq{configure sensors view} is presented.
			
	&& \req{utility cost conf view}Utility Cost Configuration View.
	
		&&& The view has a field to enter cost per kilowatt hour.
		&&& The view has a field to enter the demand charge structure.
		&&& The view has a ``Save Changes'' button.
			&&&& Pressing this button saves the configuration to the database.
			&&&& Pressing this button returns the user to the Production Configuration
			View \refreq{prod conf view}.
		&&& The view has a ``Cancel'' button.
			&&&& Pressing this button discards any changes made by the user.
			&&&& Pressing this button returns the user to the Production Configuration
			View \refreq{prod conf view}.


\end{easylist}

\setstretch{2}
%% @DocumentRequirement (9,"Signatures of all Team Members and Customer.")
\clearpage
\section{Customer Agreement}

%% @DocumentRequirement (9.1,"Names, signatures, and dates.")

The undersigned agree that the requirements outlined in this document meet all needs for the product.

\signanddate{Ben Ealey}
\signanddate{Asanga Bandara}
\signanddate{Doug Bouler}
\signanddate{Alex Chaloux}
\signanddate{F. Alex Wortham}

%% @DocumentRequirement (9.2,"Dissenting statements (signed) -- if any.")

\end{document}
